Data Analytics Introduction Using Python Training

### 2024-11-10 MsaPythonDataAnalytics.qmd
update 4

-   Mixed instructional guide, with the presentation but focused on getting more hard skills

-   Engagements and practice on the fly
:::

@@

```{python}
#| echo: false
#| eval: false

@@

@@

@@

@@

@@

## Folder Structure & File Management

# SQL

## SQL Introduction  {.smaller}

>>>>

>   Mixed instructional guide, with the presentation but focused on getting more hard skills

>   Engagements and practice on the fly
:::

@@

@@

### Pandas Data Cleaning

> 80% of the work done on data is cleaning

#### Dealing with missing data

|Method |	Description
|------|---------
|dropna |	Filter axis labels based on whether values for each label have missing data, with varying thresholds for how much missing data to tolerate.
|fillna |	Fill in missing data with some value or using an interpolation method such as "ffill" or "bfill".
|isna |	Return Boolean values indicating which values are missing/NA.
|notna	| Negation of `isna`, returns True for non-NA values and False for NA values.

#### Data Transformation

***Removing Duplicates***

data = pd.DataFrame({"k1": ["one", "two"] * 3 + ["two"],
                     "k2": [1, 1, 2, 3, 3, 4, 4]})

data.duplicated()

data.drop_duplicates()

data["v1"] = range(7)

data.drop_duplicates(subset=["k1"])

data.drop_duplicates(["k1", "k2"], keep="last")

@@

## Visualization

The point of visualization is being able to summary data to palatable chunks, easy to read and digest. Quick glances and be able to tell a story.

Humans are visual, absorbing more through image than any other thing. There are very many examples of visuals that have impacted the world I will talk about 3.

1. **The general** [minrad maps](https://bigthink.com/wp-content/uploads/2010/07/18578322.png?fit=1200,675)
2. **The nurse** [crimea wars](https://upload.wikimedia.org/wikipedia/commons/1/17/Nightingale-mortality.jpg)
3. **The Doctor** [cholera maps](https://www.esri.com/arcgis-blog/wp-content/uploads/2023/12/JohnSnowCholeraMap_Detail.png)

Any visual should be able to tell a story either for record purposes and future solutions, predictions.

## {fullscreen=true}

<iframe class="stretch" data-src="https://www.gapminder.org/tools/#$chart-type=bubbles&url=v1"></iframe>

@@

**Bar charts**

```{python}
#| echo: true
x = [10, 20, 30, 40, 50, 60]
y = [13, 45, 23, 34, 96, 76]
plt.title('Bar Graph')
plt.bar(x, y, color='dodgerblue', width=5)
plt.show()
```

**Pie charts**

```{python}
#| echo: true
x = [35, 20, 30, 40, 50, 30]
y = ['Apple', 'Bananna', 'Grapes', 'Orange', 'PineApple', 'Dragon Fruit']
plt.title('Pie Chart')
plt.pie(x, labels=y)
plt.show()

@@

Seaborn module for visualization

**Line Graph**

# importing packages
import seaborn as sns
# loading dataset
data = sns.load_dataset("iris")
# draw lineplot
sns.lineplot(x="sepal_length", y="sepal_width", data=data)

**Scatter Graph**

data = sns.load_dataset("iris")
sns.scatterplot(data=data)
```

@@

## Folder Structure & File Management {visibility="hidden"}

# SQL {visibility="hidden"}

## SQL Introduction  {.smaller} {visibility="hidden"}
